---
title: "Cross-Validation"
output: github_document
---
```{r setup, include = FALSE}
library(tidyverse)
library(purrr)
library(rvest)
library(dplyr)
library(stringr)
library(gam)
library(modelr)


knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Simulate data

```{r}
nonlin_df = 
  tibble(
    id = 1:100,
    x = runif(100, 0, 1),
    y = 1 - 10 * (x - .3) ^ 2 + rnorm(100, 0, .3)
  )
```


Look at the data

```{r}
nonlin_df %>% 
  ggplot(aes(x = x, y = y)) +
  geom_point()
```

## Cross validation -- by hand

Get training and testing datasets

```{r}
train_df = sample_n(nonlin_df, size = 80)
test_df = anti_join(nonlin_df, train_df, by = "id")
```


Fit 3 models.

```{r}
linear_mod = lm(y ~ x, data = train_df)
smooth_mod = gam(y ~ s(x), data = train_df)
wiggly_mod = gam(y ~ s(x), sp = 10e-6, data = train_df)
```


can I see what I just did...

```{r}
train_df %>% 
  gather_predictions(linear_mod, smooth_mod, wiggly_mod) %>% 
  ggplot(aes(x = x, y = y)) +
  geom_point() +
  geom_line(aes(y = pred), color = "red") +
  facet_grid(. ~ model)
```
Look at prediction accuracy

```{r}
rmse(linear_mod, test_df)
rmse(wiggly_mod, test_df)
rmse(smooth_mod, test_df)
```

## Cross validation using `modelr`

```{r}
cv_df = 
  crossv_mc(nonlin_df, 100)
```

What is happening here...

```{r}
cv_df %>% pull(train) %>% .[[1]] %>% as_tibble()
cv_df %>% pull(test) %>% .[[1]] %>% as_tibble()

```

```{r}
cv_df =
  cv_df %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  ) %>% view()
```

Let's try to fit models and get RMSEs for them.

```{r}
cv_df %>% 
  mutate(
    linear_mod = map(.x = train, ~lm(y ~ x, data = .x))
  )
```


Let's try to fit models and get RMSEs for them

```{r}
cv_df_new = 
cv_df %>% 
  mutate(
    linear_mod = map(.x = train, ~lm(y ~ x, data = .x)),
    smooth_mod = map(.x = train, ~gam(y ~ s(x), data = .x)),
    wiggly_mod = map(.x = train, ~gam(y ~s(x), sp = 10e-6, data = .x))
  ) %>% 
  mutate(
    rmse_linear = map2_dbl(.x = linear_mod, .y = test, ~rmse(model = .x, data = .y)),
    rmse_smooth = map2_dbl(.x = linear_mod, .y = test, ~rmse(model = .x, data = .y)),
    rmse_wiggly = map2_dbl(.x = linear_mod, .y = test, ~rmse(model = .x, data = .y))
  )
```

What do these results say about model choice?

```{r}
cv_df_new %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  ggplot(aes(x = model, y = rmse)) +
  geom_violin()
```

Compute averages...

```{r}
cv_df_new %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  group_by(model) %>% 
  summarize(avg_rmse = mean(rmse))
```

## Try on a real dataset.

import my data

```{r}
child_growth = 
  read_csv("./nepalese_children.csv") %>% view()
```
```{r}
child_growth %>% 
  ggplot(aes(x = weight, y = armc)) + 
  geom_point(alpha = .5)
```

Try some models

```{r}
child_growth =
  child_growth %>% 
  mutate(weight_cp = (weight > 7) * (weight - 7))

```

Fit the models I care about

```{r}
linear_mod = lm(armc ~ weight, data = child_growth)
pwlin_mod = lm(armc ~ weight + weight_cp, data = child_growth)
smooth_mod = gam(armc ~ s(weight), data = child_growth)
```

```{r}
child_growth %>% 
  gather_predictions(linear_mod, pwlin_mod, smooth_mod) %>% 
  ggplot(aes(x = weight, y = armc)) +
  geom_point(alpha = .3) +
  geom_line(aes(y = pred), color = "red") +
  facet_grid(. ~model)
```


Let's try to understand model fit using cross-validation.

```{r}
cv_df = 
  crossv_mc(child_growth, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  ) %>% view()
```

See if I can fit the models to the splits...
```{r}
#cv_df = 
#  child_growth %>% 
#  mutate(
#    linear_mod = map(.x = train, ~lm(armc ~ weight, data = .x)),
#    pwlin_mod = map(.x = train, ~lm(armc ~ weight + weight_cp, data = .x)),
#    smooth_mod = map(.x = train, ~gam(armc ~ s(weight), data = .x))
#  ) %>% 
#  mutate(
#    rmse_linear = map2_dbl(.x = linear_mod, .y = test, ~rmse(model = .x, data = .y)),
#    rmse_pwlin = map2_dbl(.x = pwlin_mod, .y = test, ~rmse(model = .x, data = .y)),
#    rmse_smooth = map2_dbl(.x = smooth_mod, .y = test, ~rmse(model = .x, data = .y))
#  )
```

